Computational Prediction of Boundaries of 3D Genomic Domains in Class Imbalance

### 2019-06-04 Manuscript/manuscript.Rmd
manuscript edits

@@

We analyzed publically available Hi-C data for the GM12878 and K562 cell lines provided by Rao et al. [@rao20143d]. Topologically associating domains were identified using the Arrowhead algorithm [@durand2016juicebox] obtained at 10 kb, 25 kb, 50 kb, and 100 kb resolutions, for each cell line respectively. We then established a unified approach toward preparing cell line specific TAD boundary data for predictive modelling purposes, irrespective of data resolutions (Figure 1).

To enable us to build a model that suitably discriminated between regions on the linear genome that were near TAD boundaries and regions that were not, we created a  resolution-specific response variable that indicated whether a genomic bin of unit width overlapped with a flanked TAD boundary ($Y=1$), or not ($Y=0$). The unit width of each bin on the linear genome corresponded to the resolution of the cell line specific contact matrix on which domains were called. Moreover, TAD boundaries were flanked on either side by the same unit length as the genomic bins to account for uncertainty in boundary location.

>>>>

## Cell line and Data Resolution Specific Model Construction

We analyzed publically available Hi-C data for the GM12878 and K562 cell lines provided by Rao et al. [@rao20143d]. Topologically associating domains were identified using the Arrowhead algorithm [@durand2016juicebox] obtained at 10 kb, 25 kb, 50 kb, and 100 kb resolutions, for each cell line respectively. We then established a unified approach toward preparing cell line and resolution specific TAD boundary data for predictive modelling purposes (Figure 1). To enable us to build a model that suitably discriminated between regions on the linear genome that were near TAD boundaries and regions that were not, we created a  resolution-specific response variable that indicated whether a genomic bin of unit width overlapped with a flanked TAD boundary ($Y=1$), or not ($Y=0$). The unit width of each bin on the linear genome corresponded to the resolution of the cell line specific contact matrix on which domains were called. Moreover, TAD boundaries were flanked on either side by the same unit length as the genomic bins to account for uncertainty in boundary location.

@@
